Solar wind predictions for the Parker Solar Probe orbit

### 2017-10-10 paperMVVB_referee/referee_report_responses.txt

Referee Report

This paper discusses a method of using OMNI and Helios solar wind data to estimate the solar wind parameters that might be expected during the upcoming Parker Solar Probe mission. It includes an estimate of how these parameters might vary with solar cycle, though this is a relatively small correction, and the likely sunspot number during the mission is anyway highly uncertain. The analysis appears to be thorough, retaining information on the log-normal distribution of the parameters that is used to produce “model” representations of the distributions and their variation during the solar cycle. However, in the end, this information isn’t used in the predictions at PSP, where only median values are considered. It’s also not clear whether this type of analysis has any advantage over say a simple-minded approach where you use the radial dependence of averaged Helios values to propagate averaged 1 AU values, perhaps taken at different times in the solar cycle, down to the PSP orbit. My suspicion is that the results might not be all that different, but the authors might like to address this point. The extrapolated values do appear to be fairly consistent with previous estimates of near Sun parameters, and deviations, e.g. in the speed profile can be plausibly accounted for, so the results appear to be reasonable.

- ...
+ use the distributions for the predictions (add perihelia figures of distributions)
+ state advantage over simple-minded approach (example of simple-minded approach; state how different the results are)

@@

Some steps in the procedure could be explained more clearly in the text, as noted below, and the tables are rather cryptic since the meaning of the various parameters is not always clear. If they are fit parameters, it would be helpful to state the function that is being fitted in the table. There are conclusions and summary sections that both, yet again, go through the analysis procedure, which is unnecessary. They could be combined. There are also useful functions that give the radial dependences of the parameters that are only shown in the summary section. They could be included in the main results section.

- ...
+ procedural steps to be explained in detail
+ clarify the meaning of the parameters in tables
+ link the fit equations in table captions
+ combine conclusion and summary sections
+ include final functions in results section

@@

- adopted
+ highlighted
+ can be adopted

Introduction, line 8: “Until today” is unnecessary – suggest removing. SOHO is also at L1 and returns solar wind observations from CELIAS. But maybe it’s not necessary to list the spacecraft, especially as other spacecraft not listed contributed earlier observations to OMNI.

- removed
+ highlighted
+ can be removed

- SOHO added
- should we keep it?
+ highlighted
+ add SOHO
+ SOHO/CELIAS not real-time (ca. +3 hours)
+ SOHO/CELIAS does not contribute to OMNI data set

@@

- adopted
+ highlighted
+ can be adopted

Page 6, Table 1:

Suggest writing the units together with the parameters in the first column, e.g. “Magnetic field (nT)”, rather than in a table footnote.

- changed
- should we keep it? doesn't it look too packed?
+ highlighted
+ can be adopted

@@

+ do that for all tables

I don’t really understand what the numbers in brackets (“estimated standard deviations”) represent. Why are they much larger than the parameter values and whole numbers?

- added notation explanation
+ highlighted
+ explain

- added notation explanation in all tables
+ explain in all tables??

+ explain also errors??

@@

How are the mean absolute errors and sums of absolute errors defined?

- mean absolute errors unnecessary (they are not referred to in paper), removed from table
+ highlighted

- explained more clearly in text and table caption
+ highlighted
+ explain

@@

Line 7: Is this “overestimation” because [I]CMEs have abnormally low, not high, temperatures?

+ highlighted
+ look into that

Page 8, last paragraph, line 2: Maybe avoid the word "correlated" since it is used below, and there is no correlation here. E.g., … fast solar wind occurs at times when polar coronal holes extend to lower latitudes, a typical feature of the declining phase of the solar cycle as pointed out by..... Therefore... exhibit time lags relative to the SSN maxima.

- adopted
+ highlighted
+ adopt
+ 'time lags' without hyphen!

@@

- adopted
+ highlighted
+ can be adopted

- changed 'lag time' to 'time lag'
+ below, change 'lag time' to 'time lag'

Page 10, Table 2: Similar comments to those for Table 1 apply.

- table caption equation references added
- in section 3 sentence with equation (9) clarified
+ highlighted
+ change

@@

Three lines below table and following: I find this step difficult to follow. It seems that the sunspot numbers are shifted according to the lags, and there is some fit to the data which is then used to produce a model of the particular parameter as a function of SSN, but the text doesn't explain the motivation (apparently to produce a "model" distribution as a function of SSN) procedure very clearly.

- explained more clearly
+ highlighted
+ explain motivation more clearly

- section 3, second sentence: abbreviated 'sunspot number'
- section 3, switched second and third paragraph
- section 3, added a sentence to now second paragraph

### 2017-10-10 paperMVVB/sections/content.tex
worked on referee comments; made changes bold face

	\caption{Resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions from near \SI{1}{\au} OMNI hourly data. For the velocity also the fit parameters of the double lognormal function (\ref{eq:double_lognormal_fit_function}) are listed, as well as the median and mean values of the resulting velocity fit. The \hl{mean absolute errors } and \hl{sums of absolute residuals } are also listed. The values in brackets are the \hl{estimated standard deviations } of the fit parameters.}

@@

		S[table-format = 2.3]

@@

		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{\multirow{1}{*}{MAE}}	&\multicolumn{1}{c}{SAR}\\
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$}	&\multicolumn{1}{c}{$x_\text{avg}$}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{[$10^{-4}$]}	&\multicolumn{1}{c}{[\%]}\\

@@

		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&5.661(16)	&6.164(18)	&--	&5.51	&6.83\\
		\multicolumn{2}{l}{\textbf{Velocity [\SI{e2}{\km\per\s}]}}	&4.085(19)	&4.183(20)	&--	&18.0	&18.69\\
		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&5.276(24)	&6.484(34)	&--	&5.49	&6.48\\
		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&7.470(17)	&11.301(32)	&--	&0.871	&5.78\\

@@

		\multirow{2}{*}{\textbf{Velocity}}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
		\multirow{2}{*}{\textbf{[\SI{e2}{\km\per\s}]}~}	&\multicolumn{1}{c}{$W_2$}	&3.68(20)	&3.72(20)	&	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
			&\multicolumn{1}{c}{$W_\text{II}$}	&4.16(14)\tablefootmark{a}	&4.42(14)\tablefootmark{a}	&\multicolumn{1}{c}{--}	&3.98	&4.20\\

@@

From visual inspection, the resulting fit curves describe the shape of the magnetic field strength, density and temperature distributions well, as can be seen in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}. However, for the velocity the fit function appears not to be as good in describing the measured distribution’s more complex shape around its peak and in the higher velocity range. This also can be inferred from the sum of absolute residuals (SAR) between data and fit listed in Table~\ref{tab:lognormal_fit_parameters}, being almost three times larger than those from the other parameters.
\begin{figure*}
	\includegraphics[width=18cm]{figures/histogram_fits_4_a_zoom_paper_pdfplot.pdf}
	\caption{Frequency distributions of the four solar wind parameters and their lognormal fits derived from the hourly OMNI data set. The histograms have bins of \SI{0.5}{\nT}, \SI{10}{\km\per\s}, \SI{1}{\per\cm\cubed} and \SI{10000}{\K}. The fits' median and mean values are indicated as well. The insets show zoomed-in \textbf{views of the high value tails of the distributions. } }
	\label{fig:histogram_fits_4_a_zoom_paper_pdfplot}
\end{figure*}

@@

\section{Solar activity dependence of the solar wind frequency distributions}
\label{sec:solar_activity_variations}
In the next step we investigate how the long-term solar wind distribution functions presented in the previous section depend on general solar activity. Therefore we examine their correlation with the sunspot number, being a commonly used long-term solar activity index, and determine the time lags with the highest correlation coefficients.

@@

%\subsection{SSN correlation}
For the correlations we fit lognormal functions to the frequency distributions as in Sect.~\ref{sec:frequency_distribution}, but implement linear relations to the yearly SSN, allowing shifting of the distribution functions with SSN. For the velocity the approach is different insofar as its two components are kept fixed and instead their balance is modified with the changing SSN.

@@

%\subsection{SSN fitting}
\hl{To enable shifts of the solar wind frequency distributions with the SSN } , we add a linear SSN dependency to the median
\begin{align}
	x_\text{med}(ssn) &= a_\text{med} \cdot ssn + b_\text{med}\,,	\label{eq:median_with_ssn}
\end{align}
using a factor to the SSN $a_\text{med}$ with a baseline $b_\text{med}$. We relate the mean with a scaling factor to the median to transfer its SSN dependency:
\begin{align}
	x_\text{avg}(ssn) &= (1 + a_\text{avg}) \cdot x_\text{med}(ssn)\,.	\label{eq:mean_with_ssn}
\end{align}
\hl{With the implementation of these relations into the lognormal function } (\ref{eq:single_lognormal_fit_function}), the new dynamic fit function $W'(x,ssn)$ is then fitted to the yearly data. The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
\begin{table*}
	\caption{Resulting fit coefficients from the OMNI data fitting with \textbf{the linear SSN dependencies (\ref{eq:median_with_ssn}) and (\ref{eq:mean_with_ssn})}. For the velocity the fit parameters from the double lognormal fit \textbf{(\ref{eq:double_lognormal_fit_function})} and their balancing function \textbf{(\ref{eq:balance_with_ssn})} are given. The values in brackets are the \hl{estimated standard deviation} of the fit parameters.}
	\label{tab:ssn_fit_parameters}
	\centering
	\begin{tabular}{l@{} c@{}
		S[table-format = 1.3(2)e+1]
		S[table-format = 1.4(2)]
		S[table-format = 1.3(2)e+1]
		S[table-format = +1.3(2)e+1]
		c
		}
		\hline\hline
		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}\\
		\cline{3-4}\cline{6-7}
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{SSN factor $a_\text{med}$}	&\multicolumn{1}{c}{Baseline $b_\text{med}$}	&\multicolumn{1}{c}{Scaling factor $a_\text{avg}$}	&\multicolumn{1}{c}{SSN factor $c_a$}	&\multicolumn{1}{c}{Baseline $c_b$}\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--\\
%		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Density}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Temperature}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--\\
		\hline
		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W'_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}\\
			&\multicolumn{1}{c}{$W'_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
	}
\end{table*}

@@

The median and mean values of the key solar wind parameters for different solar distances of the Helios data are calculated for the minimal distance resolution \SI{0.01}{\au} of the data set\hl{, see } Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}. Assuming a radial solar wind outflow, it is expected that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described through power law scaling. Therefore we use the power law function
\begin{align}
	x(r) = d\cdot r^e	\label{eq:power_function}
\end{align}
for the regression fit of the median and mean, with $r$ being the solar distance in astronomical units, $d$ the magnitude at \SI{1}{\au} and $e$ the exponent. The fits are weighted through the different data counts per bin.
%fit result table and figure
The fit coefficients ($d_\text{med}$, $d_\text{avg}$, $e_\text{med}$ and $e_\text{avg}$) are listed in Table~\ref{tab:mean_median_fit_parameter}.
\begin{table*}
	\caption{Fit coefficients for the median and mean solar distance dependencies \textbf{(\ref{eq:power_function})} of the four solar wind parameters derived from the combined Helios~1 and 2 data. The errors in brackets are the \hl{estimated standard deviations} of each fit parameter. The crossing distances indicate where the median and mean fits intersect each other. The yearly variation is the weighted standard deviation derived from the yearly fit exponents seen in Fig.~\ref{fig:yearly_gradients_c}.}
	\label{tab:mean_median_fit_parameter}
	\centering
	\begin{tabular}{l
	S[table-format = 1.3(2)]
	S[table-format = +1.3(2)]
	@{}c
	S[table-format = 1.3(2)]
	S[table-format = +1.3(2)]
	S[table-format = 1.1(2)e1]
	S[table-format = 1.3]}
		\hline\hline
		\multirow{2}{*}{Parameter}	&\multicolumn{2}{c}{Median}	&	&\multicolumn{2}{c}{Mean}	&\multicolumn{1}{c}{Crossing distance}	&\multicolumn{1}{c}{Yearly variation}\\
		\cline{2-3}	\cline{5-6}
			&\multicolumn{1}{c}{$d_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{med}$}	&	&\multicolumn{1}{c}{$d_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{avg}$}	&\multicolumn{1}{c}{[\si{\au}]}	&\multicolumn{1}{c}{$\Delta e$}\\
		\hline
		Magnetic field	&5.377(92)	&-1.655(17)	&	&6.05(10)	&-1.546(18)	&0.339(11)	&0.11\\
		Velocity	&4.107(28)	&0.058(13)	&	&4.356(24)	&0.049(10)	&0.7(83)e3	&0.012\\
		Density		&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)	&0.072\\
		Temperature	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)	&0.050\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
	}
\end{table*}
% source year variation: fit_out_yearly_gradients_table_b_stats.txt

@@

	\caption{Fit coefficients \textbf{for the distance depending single lognormal function, equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function})}, respectively double lognormal \textbf{function (\ref{eq:double_lognormal_fit_function})} for the velocity from the combined Helios data. The errors in brackets are the \hl{estimated standard deviations} of the fit parameters. The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}

>>>>

	\caption{Resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions from near \SI{1}{\au} OMNI hourly data. For the velocity also the fit parameters of the double lognormal function (\ref{eq:double_lognormal_fit_function}) are listed, as well as the median and mean values of the resulting velocity fit. \textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} \textbf{For each parameter the sum of absolute residuals between data and fit (in percentage of the distribution area) is also listed.}}

@@

@@

		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{SAR}\\
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$}	&\multicolumn{1}{c}{$x_\text{avg}$}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{[\%]}\\

@@

		\multicolumn{2}{l}{\textbf{Magnetic field [\si{nT}]}}	&5.661(16)	&6.164(18)	&--	&6.83\\
		\multicolumn{2}{l}{\textbf{Velocity [\SI{e2}{\km\per\s}]}}	&4.085(19)	&4.183(20)	&--	&18.69\\
		\multicolumn{2}{l}{\textbf{Density [\si{\per\cm\cubed}]}}	&5.276(24)	&6.484(34)	&--	&6.48\\
		\multicolumn{2}{l}{\textbf{Temperature [\SI{e4}{\K}]}}	&7.470(17)	&11.301(32)	&--	&5.78\\

@@

		\multirow{2}{*}{\textbf{Velocity}}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}\\
		\multirow{2}{*}{\textbf{[\SI{e2}{\km\per\s}]}~}	&\multicolumn{1}{c}{$W_2$}	&3.68(20)	&3.72(20)	&	&\multicolumn{1}{c}{--}\\
		\cline{2-6}
			&\multicolumn{1}{c}{$W_\text{II}$}	&4.16(14)\tablefootmark{a}	&4.42(14)\tablefootmark{a}	&\multicolumn{1}{c}{--}	&4.20\\

@@

From visual inspection, the resulting fit curves describe the shape of the magnetic field strength, density and temperature distributions well, as can be seen in Fig.~\ref{fig:histogram_fits_4_a_zoom_paper_pdfplot}. However, for the velocity the fit function appears not to be as good in describing the measured distribution’s more complex shape around its peak and in the higher velocity range. This also can be inferred from the sum of absolute residuals (SAR) between data and fit, listed in Table~\ref{tab:lognormal_fit_parameters} \textbf{in percentage of the distribution area}, being almost three times larger than those from the other parameters.
\begin{figure*}
	\includegraphics[width=18cm]{figures/histogram_fits_4_a_zoom_paper_pdfplot.pdf}
	\caption{Frequency distributions of the four solar wind parameters and their lognormal fits derived from the hourly OMNI data set. The histograms have bins of \SI{0.5}{\nT}, \SI{10}{\km\per\s}, \SI{1}{\per\cm\cubed} and \SI{10000}{\K}. The fits' median and mean values are indicated as well. The insets show zoomed-in \textbf{views of the high value tails of the distributions. } }
	\label{fig:histogram_fits_4_a_zoom_paper_pdfplot}
\end{figure*}

@@

\section{Solar activity dependence of the solar wind frequency distributions}
\label{sec:solar_activity_variations}
In the next step we investigate how the long-term solar wind distribution functions presented in the previous section depend on general solar activity. Therefore we examine their correlation with the \textbf{SSN}, being a commonly used long-term solar activity index, and determine the time lags with the highest correlation coefficients.

%\subsection{SSN correlation}
For the correlations we fit lognormal functions to the frequency distributions as in Sect.~\ref{sec:frequency_distribution}, but implement linear relations to the yearly SSN, allowing shifting of the distribution functions with SSN. For the velocity the approach is different insofar as its two components are kept fixed and instead their balance is modified with the changing SSN. \textbf{Thus we obtain on solar activity depending models for the frequency distributions of all four solar wind parameters.}

@@

@@

%\subsection{SSN fitting}
\textbf{Next we create solar activity dependent analytical representations of the solar wind frequency distributions. This is achieved by shifting the median positions of the lognormal distributions as a linear function of SSN. To enable these shifts }, we add a linear SSN dependency to the median
\begin{align}
	x_\text{med}(ssn) &= a_\text{med} \cdot ssn + b_\text{med}\,,	\label{eq:median_with_ssn}
\end{align}
using a factor to the SSN $a_\text{med}$ with a baseline $b_\text{med}$. We relate the mean with a scaling factor to the median to transfer its SSN dependency:
\begin{align}
	x_\text{avg}(ssn) &= (1 + a_\text{avg}) \cdot x_\text{med}(ssn)\,.	\label{eq:mean_with_ssn}
\end{align}
\textbf{These relations, substituted into the lognormal function (\ref{eq:single_lognormal_fit_function}), lead to a new SSN-dependent function $W'(x,ssn)$. This function} is then fitted to the yearly data\textbf{, using the yearly SSN as input parameter.} \textbf{The SSN is offset with the individual time lags for each parameter determined before, to profit from the higher correlation.} The three resulting fit coefficients ($a_\text{med}, b_\text{med}$ and $a_\text{avg}$) are presented in Table~\ref{tab:ssn_fit_parameters}.
\begin{table*}
	\caption{Resulting fit coefficients from the OMNI data fitting with \textbf{the linear SSN dependencies (\ref{eq:median_with_ssn}) and (\ref{eq:mean_with_ssn})}. For the velocity the fit parameters from the double lognormal fit \textbf{(\ref{eq:double_lognormal_fit_function})} and their balancing function \textbf{(\ref{eq:balance_with_ssn})} are given. \textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.}}
	\label{tab:ssn_fit_parameters}
	\centering
	\begin{tabular}{l@{} c@{}
		S[table-format = 1.3(2)e+1]
		S[table-format = 1.4(2)]
		S[table-format = 1.3(2)e+1]
		S[table-format = +1.3(2)e+1]
		c
		}
		\hline\hline
		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{2}{c}{Median\tablefootmark{a}}	&\multicolumn{1}{c}{Mean}	&\multicolumn{2}{c}{Balance}\\
		\cline{3-4}\cline{6-7}
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{SSN factor $a_\text{med}$}	&\multicolumn{1}{c}{Baseline $b_\text{med}$}	&\multicolumn{1}{c}{Scaling factor $a_\text{avg}$}	&\multicolumn{1}{c}{SSN factor $c_a$}	&\multicolumn{1}{c}{Baseline $c_b$}\\
		\hline
		\multicolumn{2}{l}{Magnetic field}	&1.309(19)e-2	&4.285(17)	&8.786(78)e-2	&\multicolumn{1}{c}{--}	&--\\
%		\multicolumn{2}{l}{Velocity}	&2.514(93)e-3	&3.8521(90)	&2.392(26)e-2	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Density}	&3.81(25)e-3	&4.495(26)	&3.050(27)e-1	&\multicolumn{1}{c}{--}	&--\\
		\multicolumn{2}{l}{Temperature}	&1.974(26)e-2	&5.729(19)	&6.541(28)e-1	&\multicolumn{1}{c}{--}	&--\\
		\hline
		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W'_1$}	&\multicolumn{1}{c}{--}	&3.633(12)	&1.008(37)e-2	&\multirow{2}{*}{\tablenum{-1.799(95)e-3}}	&\multirow{2}{*}{0.638(32)}\\
			&\multicolumn{1}{c}{$W'_2$}	&\multicolumn{1}{c}{--}	&4.831(81)	&2.31(20)e-2	&	&\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
	}
\end{table*}

@@

The median and mean values of the key solar wind parameters for different solar distances of the Helios data are calculated for the minimal distance resolution \SI{0.01}{\au} of the data set\hl{, see } Fig.~\ref{fig:radial_fit_4_thesis_light_b_skip}. Assuming a radial solar wind outflow, it is expected that the distance dependence of the solar wind parameters over the Helios data range \SIrange{0.29}{0.98}{\au} can be described through power law scaling. Therefore we use the power law function
\begin{align}
	x(r) = d\cdot r^e	\label{eq:power_function}
\end{align}
for the regression fit of the median and mean, with $r$ being the solar distance in astronomical units, $d$ the magnitude at \SI{1}{\au} and $e$ the exponent. The fits are weighted through the different data counts per bin.
%fit result table and figure
The fit coefficients ($d_\text{med}$, $d_\text{avg}$, $e_\text{med}$ and $e_\text{avg}$) are listed in Table~\ref{tab:mean_median_fit_parameter}.
\begin{table*}
	\caption{Fit coefficients for the median and mean solar distance dependencies \textbf{(\ref{eq:power_function})} of the four solar wind parameters derived from the combined Helios~1 and 2 data. \textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} The crossing distances indicate where the median and mean fits intersect each other. The yearly variation is the weighted standard deviation derived from the yearly fit exponents seen in Fig.~\ref{fig:yearly_gradients_c}.}
	\label{tab:mean_median_fit_parameter}
	\centering
	\begin{tabular}{l
	S[table-format = 1.3(2)]
	S[table-format = +1.3(2)]
	@{}c
	S[table-format = 1.3(2)]
	S[table-format = +1.3(2)]
	S[table-format = 1.1(2)e1]
	S[table-format = 1.3]}
		\hline\hline
		\multirow{2}{*}{Parameter}	&\multicolumn{2}{c}{Median}	&	&\multicolumn{2}{c}{Mean}	&\multicolumn{1}{c}{Crossing distance}	&\multicolumn{1}{c}{Yearly variation}\\
		\cline{2-3}	\cline{5-6}
			&\multicolumn{1}{c}{$d_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{med}$}	&	&\multicolumn{1}{c}{$d_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$e_\text{avg}$}	&\multicolumn{1}{c}{[\si{\au}]}	&\multicolumn{1}{c}{$\Delta e$}\\
		\hline
		Magnetic field	&5.377(92)	&-1.655(17)	&	&6.05(10)	&-1.546(18)	&0.339(11)	&0.11\\
		Velocity	&4.107(28)	&0.058(13)	&	&4.356(24)	&0.049(10)	&0.7(83)e3	&0.012\\
		Density		&5.61(27)	&-2.093(46)	&	&7.57(30)	&-2.010(38)	&0.027(73)	&0.072\\
		Temperature	&7.14(23)	&-0.913(39)	&	&9.67(21)	&-0.792(28)	&0.082(85)	&0.050\\
		\hline
	\end{tabular}
	\tablefoot{
		\tablefoottext{a}{\hl{In units of } \si{nT}, \SI{e2}{\km\per\s}, \si{\per\cm\cubed} and \SI{e4}{\K}.}
	}
\end{table*}
% source year variation: fit_out_yearly_gradients_table_b_stats.txt

@@

	\caption{Fit coefficients \textbf{for the distance depending single lognormal function, equation (\ref{eq:single_lognormal_fit_function}) combined with (\ref{eq:power_function})}, respectively double lognormal \textbf{function (\ref{eq:double_lognormal_fit_function})} for the velocity from the combined Helios data. \textbf{The numbers in parentheses are the estimated standard deviations of the fit parameters referred to the corresponding last digits of the quoted value.} The seasonal variations are calculated from Earth's orbital solar distance variation and the derived exponents.}
